Smart Spreading Factor Assignment for LoRaWANs

### 2019-02-28 paper.tex
prediction paraphrase

In Figure \ref{fig:collision}, a LoRaWAN network deployed with a single gateway is illustrated. Different color rings represent achievable range of different SFs from the gateway and different color circles represent selected SF of the nodes. The end devices close to the gateway will fall into lowest SF (SF7) area section. The end devices close to the gateway will probably select the lowest SF most of the time. This causes a lot of collisions between same SF transmissions. Hence the number of collisions will increase as the number of end devices close to the gateway increases.

@@

\subsection{Gateway}
LoRaWAN gateway (GW) is a device that receive/transmit packets coming from/to end nodes. A typical gateway can receive from multiple channels at the same time. gateways are usually connected to power grid, so power consumption of a gateway is insignificant in most of the deployments.

@@

In Figure \ref{fig:r_pdr}, PDR plots of various network radii are shown. Number of gateway is set to 1 and lowest SF assignment scheme is used. Increasing network radius, increases the number of under sensitivity transmissions thus decreases the PDR of network.

@@

In Table \ref{table:prediction_accuracy}, prediction accuracy of smart SVM and smart DTC schemes are presented for various network radii and number of nodes. Prediction accuracy is not directly proportional to network PDR. Correct prediction of an interfered transmission may not increase the PDR but increases the prediction accuracy. Smart DTC gives better PDR results than smart SVM, even overall SVM prediction accuracy is higher. LoRaWAN simulation usually produces imbalanced training dataset. Number of under sensitivity transmission labeled data points are less than number of successful transmission labeled data points. Number of interfered transmission labeled data points are even less then number of under sensitivity transmission labeled data points. In our case, DTC gives better prediction accuracy for interfered transmission labeled data points. Correct classification of interfered transmissions yields better network PDR results, thus smart DTC scheme gives better network PDR results.

@@

\section{Conclusion} \label{Conclusion}
In this paper, after a brief introduction about LPWAN technologies, LoRa modulation basics and spreading factor assignment issue is discussed. We present a open source discrete event simulator which is developed from scratch to study network performance of LoRaWAN and evaluate different SF assignment schemes. Moreover, we show how same SF collisions can be avoided, hence, we propose a machine learning based solutions called smart DTC scheme and smart SVM scheme. We present simulation results for the lowest SF assignment scheme and the proposed schemes. Simulation results show that, the proposed smart schemes can increase network performance for LoRaWAN networks, especially, when the nodes are deployed close to gateways.

>>>>

In Figure \ref{fig:collision}, a LoRaWAN network deployed with a single gateway is illustrated. Different color rings represent achievable range of different SFs from the gateway and different color circles represent selected SF of the nodes. The end devices close to the gateway will fall into the lowest SF (SF7) area section. The end devices close to the gateway will probably select the lowest SF most of the time. This causes a lot of collisions between same SF transmissions. Hence the number of collisions will increase as the number of end devices close to the gateway increases.

@@

\subsection{Gateway}
LoRaWAN gateway (GW) is a device that receive/transmit packets coming from/to end nodes. A typical gateway can receive from multiple channels at the same time. Gateways are usually connected to power grid, so power consumption of a gateway is insignificant in most of the deployments.

@@

In Figure \ref{fig:r_pdr}, PDR plots of various network radii are shown. Number of gateways is set to 1 and lowest SF assignment scheme is used. Increasing network radius, increases the number of under sensitivity transmissions thus decreases the PDR of network.

@@

In Table \ref{table:prediction_accuracy}, prediction accuracy of smart SVM and smart DTC schemes are presented for various network radii and number of nodes. Prediction accuracy is not directly proportional to network PDR. Correct prediction of an interfered transmission may not increase the PDR but increases the prediction accuracy. Smart DTC gives better network PDR results than smart SVM, even overall smart SVM prediction accuracy is higher. The distribution of different labeled data points in the dataset is strongly related to simulation parameters. If simulation is run with small topology radius and high number of nodes, then number of interfered transmission labeled data points increases. On the other hand, using a large topology radius in the simulation causes the number of under sensitivity transmission labeled data points to increase. We choose moderately dense network parameters to bring it closer to real world deployments. With the simulation parameters utilized in this section, simulation usually produces imbalanced dataset. Number of under sensitivity transmission labeled data points are less than number of successful transmission labeled data points. Besides, number of interfered transmission labeled data points are even less then number of under sensitivity transmission labeled data points. In this case, smart DTC predicts interfered transmission labeled data points more accurately. Correct classification of interfered transmissions yields better network PDR results, thus smart DTC scheme gives better network PDR results.

@@

\section{Conclusion} \label{Conclusion}
In this paper, after a brief introduction about LPWAN technologies, LoRa modulation basics and spreading factor assignment issue is discussed. We present an open source discrete event simulator which is developed from scratch to study network performance of LoRaWAN and evaluate different SF assignment schemes. Moreover, we show how same SF collisions can be avoided, hence, we propose a machine learning based solutions called smart DTC scheme and smart SVM scheme. We present simulation results for the lowest SF assignment scheme and the proposed schemes. Simulation results show that, the proposed smart schemes can increase network performance for LoRaWAN networks, especially, when the nodes are deployed close to gateways.
